### 2020-01-30 wuhan.tex
update author

\begin{flushleft}{
	\Large
	\textbf\newline{
		Reconciling early-outbreak preliminary estimates of the basic reproductive number: a new framework and applications to the novel coronavirus (2019-nCoV) outbreak
	}
}
\newline
\\
Sang Woo Park\textsuperscript{?}
Benjamin M. Bolker\textsuperscript{?}
David Champredon\textsuperscript{?}
Michale Li\textsuperscript{?}
Bryan T. Grenfell\textsuperscript{?}
Jonathan Dushoff\textsuperscript{?}
\\
\bigskip
\textbf{1} Department of Mathematics \& Statistics, McMaster University, Hamilton, Ontario, Canada
\\
\textbf{2} Department of Ecology and Evolutionary Biology, Princeton University, Princeton, New Jersey, USA
\\
\textbf{3} Department of Biology, McMaster University, Hamilton, Ontario, Canada
\\
\textbf{4} Agent-Based Modelling Laboratory, York University, Toronto, Ontario, Canada
\\
\textbf{5} Michael G. DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, Ontario, Canada
\\
\bigskip

@@

\newcommand{\gammdist}{\mathrm{Gamma}}
\begin{table}[t]
\begin{center}
\footnotesize
\begin{tabular}{l|l|l|l}
 & Basic reproductive number & mean generation time (days) & CV$^2$ generation time \\
\hline
Study 1 & $\gammdist(\alpha=28, \beta=28/2.6)$ & constant & constant \\
\hline
Study 2 & $\gammdist(\alpha=67, \beta=67/2.92)$ & constant & constant \\
\hline
Study 3 & $\gammdist(\alpha=1400, \beta=1400/3.8)$ & constant & constant \\
\hline
Study 4 & $\gammdist(\alpha=12, \beta=12/2.2)$ & $\mathrm{Uniform}(7, 14)$ & constant\\
\hline
Study 5 & $\gammdist(\alpha=54, \beta=54/5.47)$ & $\mathrm{Uniform}(7.6, 8.4)$ & constant\\
\hline
Study 6 & N.A.$^\ast$ & $\mathrm{Uniform}(6, 10)$ & constant\\
\hline
\end{tabular}
\end{center}
\caption{
\textbf{Probability distributions for \Ro, $\bar G$, and $\kappa$.}
We use these probability distributions to obtain a probability distribution for the exponential growth rate $r$.
The Gamma distribution is parameterized by shape $\alpha$ and rate $\beta$ parameters.
Constant distributions assume fixed values according to Table 1.
$^\ast$Study 6 effectively fits an exponential curve to the cumulative number of confirmed cases without propagating any statistical uncertainty.
Instead of modeling $\mathcal R_0$ with a probability distribution and recalculating $r$, we use $r=0.114\,\mathrm{days}^{-1}$, which explains all uncertainty in $\mathcal R_0$ they report, when combined with the range of $\bar G$ they consider.
}
\end{table}

@@

>>>>

\begin{flushleft}{
	\Large
	\textbf\newline{
		Reconciling early-outbreak preliminary estimates of the basic reproductive number: a new framework and applications to the novel coronavirus (2019-nCoV) outbreak
	}
}
\newline
\\
Sang Woo Park\textsuperscript{?}
David Champredon\textsuperscript{?}
Michael Li\textsuperscript{?}
Bryan T. Grenfell\textsuperscript{?}
Jonathan Dushoff\textsuperscript{?}
\\
\bigskip
\textbf{1} Department of ???
\\
\textbf{2} Department of ???
\\
\textbf{3} Department of ???
\\
\textbf{4} Department of ???
\\
\textbf{5} Department of ???
\\
\bigskip

@@

\newcommand{\gammdist}{\mathrm{Gamma}}
\begin{table}[t]
\begin{center}
\footnotesize
\begin{tabular}{l|l|l|l}
 & Basic reproductive number & mean generation time (days) & CV$^2$ generation time \\
\hline
Study 1 & $\gammdist(\alpha=28, \beta=28/2.6)$ & constant & constant \\
\hline
Study 2 & $\gammdist(\alpha=67, \beta=67/2.92)$ & constant & constant \\
\hline
Study 3 & $\gammdist(\alpha=1400, \beta=1400/3.8)$ & constant & constant \\
\hline
Study 4 & $\gammdist(\alpha=12, \beta=12/2.2)$ & $\mathrm{Uniform}(7, 14)$ & constant\\
\hline
Study 5 & $\gammdist(\alpha=54, \beta=54/5.47)$ & $\mathrm{Uniform}(7.6, 8.4)$ & constant\\
\hline
Study 6 & N.A.$^\ast$ & $\mathrm{Uniform}(6, 10)$ & constant\\
\hline
\end{tabular}
\end{center}
\caption{
\textbf{Probability distributions for \Ro, $\bar G$, and $\kappa$.}
We use these probability distributions to obtain a probability distribution for the exponential growth rate $r$.
The Gamma distribution is parameterized by shape $\alpha$ and rate $\beta$ parameters.
Constant distributions assume fixed values according to Table 1.
$^\ast$Study 6 uses the IDEA model \citep{fisman2013idea}, through which the authors effectively fit an exponential curve to the cumulative number of confirmed cases without propagating any statistical uncertainty.
Instead of modeling $\mathcal R_0$ with a probability distribution and recalculating $r$, we use $r=0.114\,\mathrm{days}^{-1}$, which explains all uncertainty in $\mathcal R_0$ they report, when combined with the range of $\bar G$ they consider.
}
\end{table}

@@

\section*{Acknowledgements}

We thank Ben Bolker for providing useful comments on the manuscript.
